Tesseroids: command-line tools for gravity field forward modeling in spherical coordinates

### 2014-03-28 manuscript.tex
Traded pngs for eps figures

Numerical accuracy by \citet{Ku1977}.

The gravitational potential of a tesseroid is

@@

This is a reference to Figure~\ref{fig:tesseroid}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid-split.png}
    \caption{
        Adaptive discretization for a computation point P
        of the tesseroid shown in (a) using distance/size ratios of
        (b) 0.5, (c) 1, and (d) 2.
        $d$ is the distance between the tesseroid and P.
    }
    \label{fig:split}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/spherical-shell.png}
    \caption{This is a figure caption.}
    \label{fig:shell}
\end{figure}

>>>>

Numerical accuracy by \citet{Ku1977}.
\\
The gravitational potential of a tesseroid is

@@

This is a reference to Figure~\ref{fig:tesseroid}.
\\
The above integrals are solved using the Gauss-Legendre Quadrature rule
\citep{Asgharzadeh2007}

\begin{multline}
    g_{\alpha\beta}(r,\phi,\lambda) \approx G \rho
        \frac{(\lambda_2 - \lambda_1)(\phi_2 - \phi_1)(r_2 - r_1)}{8}
        \\
        \sum\limits_{k=1}^{N^{\lambda}}
        \sum\limits_{j=1}^{N^{\phi}}
        \sum\limits_{i=1}^{N^r}
        W^r_i W^{\phi}_j W^{\lambda}_k
        I_{\alpha\beta}({r'}_i, {\phi'}_j, {\lambda'}_k )
        \\
        \alpha,\beta \in \{1,2,3\}
\end{multline}

where $W_i^r$, $W_j^{\phi}$, and $W_k^{\lambda}$
are weighting coefficients
and $N^r$, $N^{\phi}$, and $N^{\lambda}$
are the number of quadrature nodes
(i.e., the order of the quadrature),
for the radius, latitude, and longitude, respectively.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid-split}
    \caption{
        Adaptive discretization for a computation point P
        of the tesseroid shown in (a) using distance/size ratios of
        (b) 0.5, (c) 1, and (d) 2.
        $d$ is the distance between the tesseroid and P.
    }
    \label{fig:split}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/spherical-shell}
    \caption{This is a figure caption.}
    \label{fig:shell}
\end{figure}
